DATA 621 - Business Analytics and Data Mining

### 2020-11-19 HW4/HW4_Group2.Rmd
Rename file for submission
Make code order cleaner

# Summary Statistics
tabularComp <- data.table(Set = c("Training", "Testing", "PredictedEval"),
                          Min = c(min(trnYS), min(tstYS), min(evalSevFit)),
                          Median = c(median(trnYS), median(tstYS),
                                     median(evalSevFit)),
                          Max = c(max(trnYS), max(tstYS), max(evalSevFit)),
                          Mean = c(mean(trnYS), mean(tstYS), mean(evalSevFit)),
                          SD = c(sd(trnYS), sd(tstYS), sd(evalSevFit)))
tabularComp[, CV := SD / Mean, by = Set]

ggplot(data.frame(x = evalSevFit), aes(x = x)) + geom_density() +
  scale_x_continuous(labels = dollar)

knitr::kable(tabularComp, digits = 3L,
             caption = "Severity Statistics Comparison")
```

>>>>

# Kernel-smoothed density
ggplot(data.frame(x = evalSevFit), aes(x = x)) + geom_density() +
  scale_x_continuous(labels = dollar)

# Summary statistics comparison
tabularComp <- data.table(Set = c("Training", "Testing", "PredictedEval"),
                          Min = c(min(trnYS), min(tstYS), min(evalSevFit)),
                          Median = c(median(trnYS), median(tstYS),
                                     median(evalSevFit)),
                          Max = c(max(trnYS), max(tstYS), max(evalSevFit)),
                          Mean = c(mean(trnYS), mean(tstYS), mean(evalSevFit)),
                          SD = c(sd(trnYS), sd(tstYS), sd(evalSevFit)))
tabularComp[, CV := SD / Mean, by = Set]
knitr::kable(tabularComp, digits = 3L,
             caption = "Severity Statistics Comparison")
```
